Predicting Future Traffic Accident Severity using A Countrywide Traffic Accident Dataset~\cite{2019arXiv190605409M}\cite{2019arXiv190909638M}

### 2024-01-07 paper/PaperForReview.tex
fix typo

\section{Feature work}
The result shows that the highest weighted f-beta score we could get is 0.943, and the highest macro f-beta score we could get is 0.65, both results is achieved by Random Forest. Since our experiments uses default parameters for almost each models, this might indicate that the default parameters for Random Forest preform well on the dataset, but others might perform better if we tweak the parameters to better fit our datasets. In the future, we hope to tweak the parameters for each models to get the best result. Additionally, we plan to enhance prediction accuracy by incorporating external data, such as road-specific speed limits and traffic volume information. This approach aims to refine our models and further improve their performance on the given dataset.

>>>>

\section{Future work}
The result shows that the highest weighted f-beta score we could get is 0.943, and the highest macro f-beta score we could get is 0.65, both results is achieved by Random Forest. Since our experiments uses default parameters for almost each models, this might indicate that the default parameters for Random Forest preform well on the dataset, but others might perform better if we tweak the parameters to better fit our datasets. In the future, we hope to tweak the parameters for each models to get the best result. Additionally, we plan to enhance prediction accuracy by incorporating external data, such as road-specific speed limits and traffic volume information. This approach aims to refine our models and further improve their performance on the given dataset.
